\subsubsection{Reward C: Surface Non-Degeneracy}
\nestindent

\textbf{What it is.}
A continuous reward scoring how much a response resembles structured mathematical reasoning, combining two signal groups:
\begin{itemize}[nosep]
    \item \textbf{Anti-gibberish} (40\% weight): penalizes CamelCase tokens (internal capitals, e.g.\ ``MesotheliomaGarvey'') and mega-tokens ({>}15 alphabetic characters), both hallmarks of degenerate text.
    \item \textbf{Pro-coherence} (60\% weight): rewards sentence breaks with capitalization, arithmetic expressions ($\texttt{digits} \pm \texttt{digits}$), numeric content, and math-domain vocabulary (``therefore'', ``total'', ``each'', ``per'', etc.).
\end{itemize}
The final score is $R_C = 0.4 \cdot \text{anti\_gibberish} + 0.6 \cdot \text{pro\_coherence}$, clamped to $[0, 1]$.
The weights are heuristic: pro-coherence receives higher weight because anti-gibberish saturates once text is non-degenerate, while pro-coherence provides a continuous gradient toward more structured mathematical reasoning.
Responses shorter than 20 characters or fewer than 3 tokens receive 0.0.
A score near 1.0 indicates well-structured mathematical text; near 0.0 indicates gibberish or degenerate output.

Importantly, C rewards non-degeneracy without accidentally rewarding correctness.
On baseline evaluation data ($n = 10{,}462$), correct and wrong-but-parseable responses score nearly identically (0.961 vs.\ 0.969), while wrong-unparseable responses score 0.454.
The reward detects gibberish vs.\ real text, but leaves the distinction between right and wrong answers entirely to the correctness reward.

\textbf{Why we chose it.}
To address the 32.8\% text degeneration rate identified in Section~1.2: without KL regularization, the model degenerates into gibberish with no gradient signal to recover.
C serves as a lightweight, output-side proxy for the same anti-degeneration effect.

In standard RLHF, a KL divergence penalty $\beta \cdot D_\text{KL}(\pi_\theta \| \pi_\text{ref})$ prevents policy degeneration~\cite{ouyang2022training, stiennon2020summarize}; DeepSeek-R1~\cite{deepseekr1} uses a format reward alongside accuracy to maintain output structure.
A more principled alternative would be adding an explicit KL penalty to the optimizer, but this requires maintaining a reference model and modifying the training loop---outside the scope of reward design.
\nestunindent
