\subsubsection{Experimental Setup}
\nestindent

\textbf{Starting checkpoint.}
All runs begin from the Part 2 best SFT checkpoint: \texttt{a4p2-sft-metamath-swiglu} at step 24633, which achieves 15.39\% strict accuracy and 88.93\% parseable rate on GSM8K.
We use the SFT checkpoint rather than the base pretrained model because it provides a stronger starting point with basic instruction-following capability already established.

\textbf{RL configuration.}
All runs use identical hyperparameters, held constant to isolate the effect of reward composition:

\begin{itemize}[nosep]
    \item Algorithm: REINFORCE (no KL regularization, no PPO clipping)
    \item Training steps: 467
    \item Examples per step: 16, samples per example: 16
    \item Maximum generation length: 256 tokens
    \item Temperature: 1.0, top-$k$: 50
    \item Learning rates: matrix 0.02, embedding 0.2, unembedding 0.004
    \item LR schedule: linear rampdown from initial fraction to 0
    \item Advantage computation: mean subtraction (not $z$-score normalization)
\end{itemize}

\textbf{Post-training evaluation.}
All runs are evaluated with temperature=1.0 and 8 samples per problem.
Pass@k requires stochastic sampling---greedy decoding produces identical outputs $k$ times, making Pass@k meaningless.
Using a single evaluation pipeline ensures all metrics (Pass@1, Pass@8, gap, extraction failure rate, error taxonomy) are internally comparable across all 10 configurations.
Because Part~2 and Part~3 evaluate under greedy decoding, accuracy numbers are not directly comparable across parts.

\textbf{Infrastructure.}
Training runs use 8$\times$H100 GPUs on Modal with \texttt{torchrun} for DDP.
Post-training evaluation is sharded across 8 containers, each evaluating a subset of the 1319 GSM8K test problems.
All training metrics are logged to W\&B (project: \texttt{490-autobook-a4}).
\nestunindent
