\textbf{Reward C: Surface Non-Degeneracy.}
C produces \pFourSeparateCDeltaPassOne{}pp Pass@1 (\pFourBaselinePassOne\% $\to$ \pFourSeparateCPassOne\%) and the second-largest reduction in extraction failures (\pFourBaselineExtrFail\% $\to$ \pFourSeparateCExtrFail\%).
Its anti-gibberish mechanism eliminates both incoherent responses and poorly-formatted ones simultaneously, explaining why it outperforms format compliance (A) despite not directly targeting format: ``no answer'' drops from \pFourBaselineNoAnswer\% to \pFourSeparateCNoAnswer\% ($-$18.1pp).

Training dynamics reinforce this: C peaks late (step 785) with sustained improvement, unlike the early-peak-then-decline pattern of binary rewards (A, D).
This suggests that C provides a smoother optimization landscape---there is always a gradient from less to more well-formed text, whereas binary rewards quickly saturate.
The net problem delta (+\pFourSeparateCNet, from \pFourSeparateCGained{} gained and \pFourSeparateCLost{} lost) confirms meaningful improvement.

\textbf{Reward D: Entity Grounding.}
Entity grounding provides \pFourSeparateDDeltaPassOne{}pp improvement (\pFourBaselinePassOne\% $\to$ \pFourSeparateDPassOne\%), just at the significance threshold.
The entity grounding component maintains a high value throughout training (0.871 at end), suggesting that once the model produces well-formed text, it naturally references question entities---D reinforces an existing tendency rather than teaching a new behavior.
The C+D combination (\pFourCombinedCdPassOne\% Pass@1) does not exceed C alone (\pFourSeparateCPassOne\%), though C+D achieves the highest Pass@8 among pairs (\pFourCombinedCdPassEight\%), indicating D contributes diversity of correct solutions.

\textbf{Reward E: Number Grounding.}
Number grounding is the strongest individual reward at \pFourSeparateEDeltaPassOne{}pp (\pFourBaselinePassOne\% $\to$ \pFourSeparateEPassOne\%), with the highest individual net gain (+\pFourSeparateENet, from \pFourSeparateEGained{} gained and only \pFourSeparateELost{} lost---the fewest losses of any reward).
E achieves format-failure reduction comparable to C: ``no answer'' drops to \pFourSeparateENoAnswer\% and ``format only'' to \pFourSeparateEFormatOnly\%.
This is surprising---number grounding does not directly target format, but rewarding responses that contain the question's numbers implicitly encourages structured mathematical text with parseable answers.

E's strength relative to D likely reflects its universal coverage: every GSM8K question contains numbers, while $\sim$3--5\% lack proper nouns.
Additionally, number overlap is a stronger necessary condition for correct problem-solving than entity overlap, since the model must use the question's specific values in its calculations.
