\subsubsection{Reward Interactions}

We analyze interaction effects by comparing combined runs to their constituent individual rewards.

\paragraph{A+B: Mild interference.}
The combined A+B run (+2.2pp) underperforms the best individual component A (+2.6pp) by 0.4pp.
This mild interference may stem from the proximity reward (B) providing noisy gradient that dilutes the format reward's cleaner signal.
Notably, A+B's sequence length follows the baseline's declining trend rather than A's increasing trend, suggesting B's signal dominates the length dynamics.

\paragraph{C+D: Additive on Pass@1, synergistic on Pass@8.}
C+D (12.8\% Pass@1) approximately equals C alone (12.9\%), indicating no Pass@1 synergy.
However, C+D achieves higher Pass@8 (37.8\% vs.\ C's 36.2\%), suggesting D contributes diversity of correct solutions.
The extraction failure rate improves further (22.8\% vs.\ C's 25.3\%).

\paragraph{C+D+E: Best knowledge ceiling.}
Adding number grounding to C+D yields the highest Pass@8 of any configuration (39.1\%) and the lowest extraction failure rate (15.9\%).
However, Pass@1 (13.1\%) is lower than E alone (13.8\%), suggesting that the three grounding rewards together create a conservative policy that solves more problems but less reliably on the first attempt.
The 26.0pp Pass@8--Pass@1 gap (the widest of any run) supports this interpretation.
Zero gibberish responses and only 3.6\% ``no answer'' failures confirm that C+D+E nearly eliminates surface-level degeneration.

\paragraph{Combined all: Constructive composition.}
The combined all run (14.6\% Pass@1, +4.9pp) substantially exceeds any individual reward or pair.
For comparison, the sum of individual improvements is A(+2.6) + B(+0.7) + C(+3.2) + D(+2.0) + E(+4.1) = +12.6pp, while the actual combined improvement is +4.9pp.
This sub-additivity is expected: the rewards target overlapping failure populations, so their effects are partially redundant.
However, the combined run gains 113 problems (more than any individual) while losing only 49, indicating that the rewards access complementary subsets of solvable problems.

\paragraph{Loss stability.}
A striking pattern across all ten configurations: the number of lost problems (relative to baseline) is remarkably stable at 44--55, regardless of which or how many rewards are used.
This suggests a fixed population of $\sim$50 problems that become harder under any reward perturbation---possibly problems whose solutions depend on behaviors that additional reward signals disrupt.
The gains, by contrast, scale with reward count (individual: 55--98, pairs: 77--96, triples: 96, full: 113), driving net improvement.
