\input{component/figures/p4/p4_macros}

\section{Part 4: Additional Reward Functions}
\nestindent

    \input{component/part4/1-introduction/introduction}

    \input{component/part4/2-eda/eda}

    \input{component/part4/2-reward-design/reward-design}

    \input{component/part4/3-methodology/methodology}

    \input{component/part4/4-results/results}

    \input{component/part4/5-discussion/discussion}

    \input{component/part4/6-conclusion/conclusion}

    \subsection{Limitations}
    \nestindent
        \input{component/part4/7-limitations/limitations}
    \nestunindent

    \newpage
    \subsection{Part 4 References}
    \nestindent
    \renewcommand{\refname}{}
    \vspace{-2em}
    \begin{thebibliography}{11}

        \bibitem{ng1999reward}
        Ng, A.~Y., Harada, D., and Russell, S.~J.
        ``Policy invariance under reward transformations: Theory and application to reward shaping.''
        \textit{Proc.\ ICML}, 1999.

        \bibitem{stiennon2020summarize}
        Stiennon, N., Ouyang, L., Wu, J., et~al.
        ``Learning to summarize from human feedback.''
        \textit{NeurIPS}, 2020.
        \url{https://arxiv.org/abs/2009.01325}

        \bibitem{ouyang2022training}
        Ouyang, L., Wu, J., Jiang, X., et~al.
        ``Training language models to follow instructions with human feedback.''
        \textit{NeurIPS}, 2022.
        \url{https://arxiv.org/abs/2203.02155}

        \bibitem{nan2021entity}
        Nan, F., Nallapati, R., Wang, Z., et~al.
        ``Entity-level factual consistency of abstractive text summarization.''
        \textit{Proc.\ EACL}, 2021.
        \url{https://arxiv.org/abs/2102.09130}

        \bibitem{gao2024reward}
        Gao, J., et~al.
        ``On designing effective RL reward at training time for LLM reasoning.''
        \textit{arXiv preprint arXiv:2410.15115}, 2024.
        \url{https://arxiv.org/abs/2410.15115}

        \bibitem{deepseekr1}
        DeepSeek-AI.
        ``DeepSeek-R1: Incentivizing reasoning capability in LLMs via reinforcement learning.''
        \textit{arXiv preprint arXiv:2501.12948}, 2025.
        \url{https://arxiv.org/abs/2501.12948}

        \bibitem{coste2024ensemble}
        Coste, T., Anwar, U., Kirk, R., and Krueger, D.
        ``Reward model ensembles help mitigate overoptimization.''
        \textit{Proc.\ ICLR}, 2024.
        \url{https://arxiv.org/abs/2310.02743}

        \bibitem{uesato2022solving}
        Uesato, J., Kushman, N., Kumar, R., et~al.
        ``Solving math word problems with process- and outcome-based feedback.''
        \textit{arXiv preprint arXiv:2211.14275}, 2022.
        \url{https://arxiv.org/abs/2211.14275}

        \bibitem{gsm8k_rlvr}
        GSM8K-RLVR Benchmark.
        \url{https://huggingface.co/datasets/allenai/gsm8k-rlvr}

        \bibitem{verl}
        veRL: Volcano Engine Reinforcement Learning for LLMs.
        \url{https://github.com/volcengine/verl}

        \bibitem{unsloth}
        Unsloth AI.
        ``GRPO and reward functions for RL fine-tuning.''
        \url{https://unsloth.ai/docs/get-started/reinforcement-learning-rl-guide}

    \end{thebibliography}
    \nestunindent

    \newpage
    \input{component/part4/8-codebase/codebase}

\nestunindent
